Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-10 paper-2023-acsos-pulverization.tex
introduce eval

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{listing-style}

@@

The pulverization approach tries to solve the problem of the deployment independence of the system, in heterogeneous infrastructures.
%
The dynamic reconfiguration of the system is a key point to achieve flexibility and adaptability of the system on the requirements changing.
%
In this section are presented two case studies that show the effectiveness of the approach:
the first case study shows the operation of the framework in a small-scale scenario, while the second case study simulate a large-scale scenario
using the framework in a simulated environment showing the effectiveness of the approach in many different conditions.

\subsection{Metrics}
\meta{descrizione}

@@

@@

\subsection{Large scale: smart city application}
\cite{PianiniJOS2013}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{listing-style}
\usepackage[hidelinks]{hyperref}

@@

In this section,
we exercise the proposed framework with two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for a urban event
and show how the dynamic reconfiguration may help achieving balance between energy consumption and QoS\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments have been released with a permissive open-source license and have been archived for future reference on Zenodo~\cite{TBD}.

\subsection{Large scale: smart city application}

\cite{PianiniJOS2013}

\subsubsection{Free variables}

@@

\subsubsection{Metrics}

@@

\subsubsection{Results}
